\section*{Acknowledgment}

Repository for this project are available at: \url{https://github.com/Rice-MECE-Capstone-Projects/Autodrone} \\

Documents and tutorial for this project are available at: \url{https://riceautodrone.github.io/} \\

% \section*{References}

\begin{thebibliography}{00} 
\bibitem{b1} ``United States Honey Bee Colony Losses 2020-2021: Preliminary Results,'' Bee Informed, Jun. 21, 2021, https://beeinformed.org/2021/06/21/united-states-honey-bee-colony-losses-2020-2021-preliminary-results.

\bibitem{b2} ``FAO - News Article: Declining bee populations pose threat to global food security and nutrition,'' Food and Agriculture Organization of the United Nations, May 20, 2019, https://www.fao.org/news/story/en/item/1194910/icode.

\bibitem{b3} K. Ma, P. Chirarattananon, S. Fuller, R. Wood, ``Controlled Flight of a Biologically Inspired, Insect-Scale Robot,'' Science Magazine, vol.340, no. 6132, pp. 603-607, May 2013.

\bibitem{b4} N. Ohi et al., ``Design of an Autonomous Precision Pollination Robot,'' 2018 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2018, pp. 7711-7718, doi: 10.1109/IROS.2018.8594444.

\bibitem{b5} M. T. Pratama et al., ``Deep Learning-based Object Detection for Crop Monitoring in Soybean Fields,'' 2020 International Joint Conference on Neural Networks (IJCNN), 2020, pp. 1-7, doi: 10.1109/IJCNN48605.2020.9207400.

\bibitem{b6} Z. Sun, X. Guo, Y. Xu, S. Zhang, X. Cheng, Q. Hu, W. Wang, and X. Xue, ``Image recognition of male oilseed rape (brassica napus) plants based on convolutional neural network for UAAS navigation applications on supplementary pollination and aerial spraying,'' Agriculture, vol. 12, no. 1, p. 62, 2022, doi: 10.3390/agriculture12010062. 

\bibitem{b7} J. Redmon, S. Divvala, R. Girshick, A. Farhadi, ``You Only Look Once: Unified, Real-Time Object Detection,'' 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), May 2016, doi: 10.1109/cvpr.2016.91.

\bibitem{b8} G. Jocher et al., ultralytics/yolov5: v6.1 - TensorRT, TensorFlow Edge TPU and OpenVINO Export and Inference (v6.1). Zenodo, 2022, doi: 10.5281/zenodo.6222936.

\bibitem{b9} "Knowledge Distillation." Wikipedia, Wikimedia Foundation, 23 Apr. 2023, en.wikipedia.org/wiki/Knowledge\_distillation. Accessed 24 Apr. 2023.

\bibitem{b10} R. Ranftl, K. Lasinger, D. Hafner, K. Schindler, and V. Koltun, ``Towards Robust Monocular Depth Estimation: Mixing Datasets for Zero-Shot Cross-Dataset Transfer,'' IEEE Transactions on Pattern Analysis and Machine Intelligence, 2019, vol. 44, no. 3, pp. 1623–1637, doi: https://doi.org/10.48550/arXiv.1907.01341

\end{thebibliography}
\vspace{12pt}

%\bibitem{b1} N. Ohi et al., ``Design of an Autonomous Precision Pollination Robot,'' unpublished.
%\bibitem{b2} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.