\section{Discussion}

This semester's achievements in drone technology demonstrate remarkable progress, especially in hardware and software integration. The successful launch of the 4-axis plane with custom PCB is a testament to our ability in advanced UAV design and integration. Coupled with this, the implementation of Software In The Loop (SITL) for simultaneous object detection and drone control, along with the camera-LiDAR fusion, has significantly enhanced the drone's environmental awareness and operational efficiency. The application of the YOLOv8 model for mask detection further emphasizes our commitment to integrating cutting-edge AI into practical solutions.

% Challange
However, challenges still remain, particularly in achieving seamless integration and operational consistency across diverse environmental conditions. The complexity of real-world scenarios often presents unforeseen obstacles, such as variable lighting, unpredictable weather, and dynamic obstacles, which can affect the drone's performance. Moreover, ensuring consistent and reliable data processing from the fusion of camera and LiDAR inputs remains a technical challenge, requiring further refinement of our algorithms and sensor calibration methods. Another challenge is that the power consumption for the whole system is insufficient, causing the drone to shut down a few seconds after take off. Addressing these challenges will be crucial for advancing the drone's capabilities and ensuring its applicability in a wider range of scenarios.

% Future plan
Looking forward, the focus will be on enhancing the drone's autonomous functions and decision-making algorithms to tackle more complex tasks and adapt to changing environments. We aim to move from using the SITL simulation to testing with a real drone. A key goal is to make the drone use less power and fly longer distances, which might mean looking into new kinds of energy or better batteries. Adding more sensors and ways to communicate could also help the drone be used in more areas, like checking the environment or helping in emergencies. By continually developing and refining these systems, our team's objective is always to keep the drone technology advanced and reliable for a variety of uses.
