\section*{Acknowledgment}

Repository for this project are available at: \url{https://github.com/Rice-MECE-Capstone-Projects/Autodrone} \\

Documents and tutorial for this project are available at: \url{https://riceautodrone.github.io/} \\

% \section*{References}

\begin{thebibliography}{00} 
\bibitem{1a1} Zhangqiang Ming, Min Zh, Xiangkun Wang, Jiamin Zhu, Junlong Cheng, Chengrui Gao, Yong Yang, Xiaoyong Wei, "Deep learning-based person re-identification methods: A survey and outlook of recent works", DOI:\url{https://ar5iv.labs.arxiv.org/html/2110.04764}

\bibitem{2c1} J. Redmon, S. Divvala, R. Girshick, A. Farhadi, ``You Only Look Once: Unified, Real-Time Object Detection,'' 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), May 2016, DOI: 10.1109/cvpr.2016.91.

\bibitem{2c2} G. Jocher et al., ultralytics/yolov5: v6.1 - TensorRT, TensorFlow Edge TPU and OpenVINO Export and Inference (v6.1). [Zenodo], 2022, DOI: 10.5281/zenodo.6222936.

\bibitem{2c3} Jocher, G., Chaurasia, A., Qiu, J. (2023). YOLO by Ultralytics (Version 8.0.0) [Computer software], DOI: \url{https://github.com/ultralytics/ultralytics}

\bibitem{2c4} Cabani, A., Hammoudi, K., Benhabiles, H., Melkemi, M. (2021), MaskedFace-Net – A dataset of correctly/incorrectly masked face images in the context of COVID-19. Smart Health, 19, 100144, DOI: \url{https://doi.org/10.1016/j.smhl.2020.100144}

\bibitem{2d1} RoboPeak Team. (2014). rplidar{\_}ros (Version master) [Computer software]. \url{https://github.com/Slamtec/rplidar_ros}

\bibitem{2e1} Gazebo Tutorials. (2023). Example World [Online tutorial]. \url{https://classic.gazebosim.org/tutorials?tut=static_map_plugin&cat=build_world#ExampleWorld}

\bibitem{2e2} Intelligent-Quads. (2023). iq{\_}gnc (Version master) [Computer software]. \url{https://github.com/Intelligent-Quads/iq_gnc/tree/master}


\end{thebibliography}
\vspace{12pt}

